
;Change this table to change how things are sorted when not using AMCM or when "Use sortingplus.ltx" is checked in the AMCM menu.

[item_kind_order]
favorites           = -2 ;custom category items set to via key bind
loadout				= -1 ;support for ARM
mags				= 0  ;support for ARM
w_sniper            = 1 
w_rifle             = 1 
w_smg               = 1
w_shotgun           = 1 
w_pistol            = 1 
w_melee             = 1
w_misc              = 1
w_base              = 1
w_explosive         = 1
o_heavy             = 2 
o_sci               = 2 
o_medium            = 2 
o_light             = 2 
o_helmet            = 2
i_arty              = 3
i_arty_junk         = 3
i_arty_cont         = 3
i_device            = 4
i_tool              = 5
i_repair            = 5
i_kit               = 5
i_backpack          = 5
i_medical           = 6
i_food              = 7
i_drink             = 7
i_mutant_cooked     = 7
i_mutant_raw        = 7
i_letter            = 8
i_quest             = 8
w_ammo              = 9
i_mutant_belt       = 10
i_mutant_part       = 10
i_misc              = 11
i_upgrade           = 12
i_part              = 13
faction_patch       = 14
junk                = 100 ;custom category items set to via key bind

;You can force some items to be sorted as a different "kind" so they are grouped together with other items with perceived similarity.
;Below are some opinionated defaults. If you add a brand new "kind" entry, (like "faction_patch") be sure to also add it to [item_kind_order] section above.

[kind_overrides]
hand_watch          = i_device
wpn_binoc_inv       = i_device
good_psy_helmet     = i_device
bad_psy_helmet      = i_device
decoder             = i_device
attackers_pda       = i_device
lead_box            = i_tool
csky_patch          = faction_patch
dolg_patch          = faction_patch
ecolog_patch        = faction_patch
freedom_patch       = faction_patch
stalker_patch       = faction_patch
bandit_patch        = faction_patch
monolith_patch      = faction_patch
army_patch          = faction_patch
killer_patch        = faction_patch
renegade_patch      = faction_patch
isg_patch           = faction_patch
greh_patch          = faction_patch

; this section describes the catagories used in the second half of the AMCM menu. This section is for modders to add new item types added by 
;		thier mod to the existing catagories or even add new ones. When adding new catagories you must make translation strings in 
;		configs/text/eng and configs/text/rus see existing strings for formatting. The leading number is the default value, position in the list
;		equates to position. NO WHITE SPACE!
[sortingplusmcm]
000favorites      = -2,favorites;custom category items set to via key bind
001loadout		  = -1,loadout;support for ARM
002mags		 	  = 0,mags;support for ARM
010weapons        = 1,w_sniper,w_rifle,w_smg,w_shotgun,w_pistol,w_melee,w_misc,w_base,w_explosive
020outfits        = 2,o_heavy,o_sci,o_medium,o_light,o_helmet,i_backpack
030artifacts      = 3,i_arty,i_arty_junk,i_arty_cont
040devices        = 4,i_device
050tools          = 5,i_tool,i_repair,i_kit
060medical        = 6,i_medical
070foods          = 7,i_food,i_drink,i_drink
080mutantfoods    = 7,i_mutant_cooked,i_mutant_raw
090quest          = 8,i_quest
100notes          = 8,i_letter
110ammo           = 9,w_ammo
120mutantparts    = 10,i_mutant_belt,i_mutant_part
130misc           = 11,i_misc
140upgrades       = 12,i_upgrade
150parts          = 13,i_part
999junk           = 100,junk;custom category items set to via key bind
